Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-11-18 bbbq_article.tex

We define a protein to be a binder if, for a certain haplotype, 
any of its 9-mer or 14-mer peptides have an IC50 value in the lowest 2\% of 
all peptides within a \emph{proteome} 
(see supplementary Tables \ref{tab:ic50_binders_mhc1} and \ref{tab:ic50_binders_mhc2} for values), 
this differs from our previous study where we defined
a binder as having an IC50 in the lowest 2\% 
of the peptides within a \emph{protein}.
% See https://github.com/richelbilderbeek/bianchi_et_al_2017/blob/72e6755a31d400158368509fd80a41e984677ab1/predict-binders.R#L17
This revised definition precludes bias of proteins 
that give rise to no or only very few MHC epitopes.
To verify that the results are similar, a side by side comparison was performed shown in the supplementary materials. \textbf{GEERT: where? give reference to figure}

@@

  \caption{
    \textbf{
      Robust prediction that TMH epitopes are presented \emph{in vivo}.
    }
    The percentage of epitopes for MHC-I and -II alleles
    that overlap with TMHs that are presented.
    Alleles are listed in Table \ref{tab:haplotype_abbreviations}).
    \textbf{(A)} 
    Observed and predicted percentage of TMH-derived epitopes
    The pair of horizontal red lines in each plot indicate the lower and upper bound 
    of the 99\% confidence interval.
    \textbf{(B)} 
    MHC ligands from IEDB binding to TMH-derived epitopes.
    The numbers above the bars denotes the number of epitopes
    obtained using an MHC ligand assay. 
  }
  \label{fig:elution}
\end{figure}

>>>>

We define a protein to be a binder if, for a certain haplotype, 
any of its 9-mer or 14-mer peptides have an IC50 value in the lowest 2\% of 
all peptides within a \emph{proteome} 
(see supplementary Tables \ref{tab:ic50_binders_mhc1} and \ref{tab:ic50_binders_mhc2} for values), 
this differs from our previous study where we defined
a binder as having an IC50 in the lowest 2\% 
of the peptides within a \emph{protein}.
% See https://github.com/richelbilderbeek/bianchi_et_al_2017/blob/72e6755a31d400158368509fd80a41e984677ab1/predict-binders.R#L17
This revised definition precludes bias of proteins 
that give rise to no or only very few MHC epitopes.
To verify that the results are similar, a side by side comparison was performed shown in the supplementary materials, Figures \ref{fig:bianch_et_al_2017_1a}
and \ref{fig:bilderbeek_et_al_2021_1a}.

@@

  \caption{
    \textbf{
      Robust prediction that TMH epitopes are presented \emph{in vivo}.
    }
    The percentage of epitopes for MHC-I and -II alleles
    that overlap with TMHs that are presented.
    Alleles are listed in Table \ref{tab:haplotype_abbreviations}).
    \textbf{(A)} 
    Observed and predicted percentage of TMH-derived epitopes
    The pair of horizontal red lines in each plot indicate the lower and upper bound 
    of the 99\% confidence interval. Note that only one line is visible as this
    interval is relatively narrow.
    \textbf{(B)} 
    MHC ligands from IEDB binding to TMH-derived epitopes.
    The numbers above the bars denotes the number of epitopes
    obtained using an MHC ligand assay. 
  }
  \label{fig:elution}
\end{figure}
